---
title: "projet_single_cell"
author: "Rahma BAAZIZ & Sandrine VRIGNON"
date: "2024-12-17"
output: html_document
---

## Installation library t

```{r}
library(dplyr)
library(Seurat)
library (patchwork)
install.packages("BiocManager")
BiocManager::install("SingleCellSignalR")
```

## Visualisation des données

Malgré le fait que les données utilisée soient normalisées, il est toujours important de pouvoir visualiser les données avant manipulation

```{r}
data<-readRDS("C://Users//sandr//OneDrive//Bureau//Cours fac//M2//Bioanalyse, transcriptomique//Single cell//dossier//myeloid-cells.RDS")
data[["percent.mt"]] <- PercentageFeatureSet(data, pattern="^MT-")  
VlnPlot(data, features=c("nFeature_RNA"), ncol=1)
VlnPlot(data, features=c("nCount_RNA"), ncol=1)
VlnPlot(data, features=c("percent.mt"), ncol=1)
```

<http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
